Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-23 WSSSPE3/report/WSSSPE3_review.tex
Section 3: keynote: Response to Dan's note to make merely one point.

Turk reminded the audience that the volunteer model means unpaid labor. On this note, he recommended Ashe
Dryden's blog
post\footnote{http://www.ashedryden.com/blog/the-ethics-of-unpaid-labor-and-the-oss-community}
on the ethics of unpaid labor and the open source software community, which
mentions GitHub as one's resume, for example. \katznote{I don't think I understand the point in the previous sentence - maybe there are multiple points and this should be broken in multiple sentences?} Often times, a person funded to
work full time on some scientific project can spend a small amount of time for working
on a piece of software necessary for the project. However, all researchers' ability
to participate in that volunteer community are not always the same and may not
always be aligned with the research projects. From Turk's experience, we cannot
always rely on unpaid labor and volunteer time to sustain a piece of
software---this came down to the notions of the top-down and the bottom-up
approaches, the funded versus the grassroots.

>>>>

Turk reminded the audience that the volunteer model means unpaid labor. On this
note, he recommended Ashe Dryden's blog
post\footnote{http://www.ashedryden.com/blog/the-ethics-of-unpaid-labor-and-the-oss-community}
on the ethics of unpaid labor and the open source software community. Often
times, a person funded to work full time on some scientific project can spend a
small amount of time for working on a piece of software necessary for the
project. However, all researchers' ability to participate in that volunteer
community are not always the same and may not always be aligned with the
research projects. From Turk's experience, we cannot always rely on unpaid labor
and volunteer time to sustain a piece of software---this came down to the
notions of the top-down and the bottom-up approaches, the funded versus the
grassroots.
